The development of children's ability to track and predict turn structure in conversation

### 2015-11-28 paper/CasillasFrank-Anticip.tex
E2 summary draft added

Each recording session began with a 20-minute warm-up period of spontaneous conversation during which the pair talked for five minutes on four topics (favorite foods, entertainment, hometown layout, and pets). Then we asked talkers to choose a new topic---one relevant to young children (e.g., riding a bike, eating breakfast)---and to improvise a dialogue on that topic. We asked them to speak as if they were on a children's television show in order to elicit child-directed speech toward each other. We recorded until the talkers achieved at least 30 seconds of uninterrupted discourse with enthusiastic, child-directed speech. Most talker pairs took less than five minutes to complete the task, usually by agreeing on a rough script at the start. We encouraged talkers to ask at least a few questions to each other during the improvisation. The resulting conversations were therefore not entirely spontaneous, but were as close as possible while still remaining child-oriented in topic, prosodic pattern, and lexicosyntactic construction.\footnote{All of the non-English talkers were fluent in English as a second language, and some fluently spoke a third or more language. We chose male-female pairs as a natural way of creating contrast between the two talker voices. See an example run-though of the videos here: }

@@

Participants looked at the screen most of the time during video playback (81\% and 91\% on average for children and adults, respectively). They primarily kept their eyes on the person who was currently speaking in both English and non-English videos: They gazed at the current speaker between 38\% and 63\% of the time, looking back at the addressee between 15\% and 20\% of the time (Table \ref{tab:e1_look}). Even three-year-olds looked more at the current speaker than anything else, whether the videos were in a language they could understand or not. Children looked at the current speaker less than adults did during the non-English videos. Despite this, their looks to the addressee did not increase substantially in the non-English videos, indicating that their looks away were probably related to boredom rather than confusion about ongoing turn structure. Overall, participants' pattern of gaze to current speakers indicated that they performed basic turn tracking during the videos, regardless of language.

@@

We identified anticipatory gaze switches for all 36 usable turn transitions, based on the criteria outlined in Section \ref{sec:algorithm}, and analyzed them for effects of language, transition type, and age with two mixed-effects logistic regressions \citep{lme4, R}. We built one model each for children and adults. We modeled children and adults separately because effects of age are only pertinent to the children's data. The child model included condition (English vs. non-English)\footnote{Because each non-English language was represented by a single stimulus, we cannot treat individual languages as factors. Gaze behavior might be best for non-native languages that have the most structural overlap with participants' native language: English speakers can make predictions about the strength of upcoming Swedish prosodic boundaries nearly as well as Swedish speakers do, but Chinese speakers are at a disadvantage in the same task \citep{carlson2005}. We would need multiple items from each of the languages to check for similarity effects of specific linguistic features.}, transition type (question vs. non-question), age (3, 4, 5), and duration of the inter-turn gap (seconds, e.g., 0.441) as predictors, with full interactions between condition, transition type, and age.  We included the duration of the inter-turn gap as a predictor since longer gaps also provide more opportunities to make anticipatory switches (Figure \ref{fig:criterion}). We additionally included random effects of item (turn transition) and participant, with random slopes of condition, transition type, and their interaction for participants \citep{barr2013}.\footnote{The models we report are all qualitatively \textit{unchanged} by the exclusion of their random slopes. We have left the random slopes in because of minor participant-level variation in the predictors modeled.} The adult model included condition, transition type, duration, and their interactions as predictors with participant and item included as random effects and random slopes of condition, transition type, and their interaction for participant.

@@

We estimated the probability that these patterns were the result of random looking by running the same regression models on participants' real eye-tracking data, only this time calculating their anticipatory gaze switches with respect to randomly permuted turn transition windows. This process involved: (1) randomizing the order and temporal placement of the analysis windows within each stimulus (Figure \ref{fig:shuffling}; the analysis window is defined in Figure \ref{fig:criterion}), thereby randomly redistributing the analysis windows across the eye-tracking signal, (2) re-running each participant's eye tracking data through switch identification (described in \ref{sec:algorithm}), but this time using the randomly permuted analysis windows, and (3) modeling the anticipatory gazes from the randomly permuted data with the same statistical models we used for the original data (Section \ref{sec:models1}; Table \ref{tab:E1-models}). Importantly, although the onset time of each transition was shuffled within the eye-tracking signal, the other intrinsic properties of each turn transition (e.g., prior speaker identity, transition type, gap duration, language condition, etc.) stayed constant across each randomly permuted version of the data.

@@

\paragraph{Developmental effects}
The model of the children's data revealed a significant interaction of age and language condition (tab:E1-models) that was highly unlikely to have derived from random looking (Figure \ref{fig:E1-randvsreal}). To further explore this effect, we compared the average effect of language condition across all ages: we extracted the average difference score for the two language conditions (English minus non-English) for each subject, computing an overall average for each random permutation of the data. For each random permutation, we then made pairwise comparisons of the average difference scores across ages. Figure \ref{fig:E1-lgageinteraction} plots the real-data difference scores against the random-data difference score distribution for each pairwise age comparison, showing that 3- and 4-year olds were affected equally by language condition, but that 5-year-olds affected less than both 3- and 4-year-olds (with 99.52\% and 99.96\% of difference scores greater than the randomly permuted data, respectively, i.e., differences of \textit{p} $<$ .01 and \textit{p} $<$ .001).

@@

Children and adults spontaneously tracked the turn structure of the conversations, making anticipatory gaze switches at an above-chance rate across all ages and conditions (Table \ref{tab:e1_look} ; Figure \ref{fig:E1-randvsreal}). Children's anticipatory gaze rates were affected by language condition, transition type, age, and gap duration (Table \ref{tab:E1-models}), none of which could be explained by a baseline of random gaze switching (Figure \ref{fig:E1-ChiTs}).

Language condition (English vs. non-English) affected children's anticipations in two ways (Table \ref{tab:E1-models};  Figure \ref{fig:E1-randvsreal}). First, children made more anticipatory switches overall in English videos, compared to non-English videos. This effect suggests that lexical access is important for children's ability to anticipate upcoming turn structure; children had no lexical access to the speech in the non-English videos, though they did have access to (non-native) prosodic cues and non-verbal behavior, consistent with prior work on turn-end prediction in adults (\citealp{de-ruiter2006}; \citealp{magyari2012}) and children \citep{keitel2013}. Second, children systematically made more anticipatory switches after hearing a question compared to a non-question, but only in the English condition, suggesting that, when children have access to lexical cues, they are more likely to make an anticipatory gaze switch when they can expect an immediate response from the addressee (i.e., an answer). In itself, this explanation also suggests that children are picking up on lexical cues to questionhood in anticipating upcoming answers (e.g., subject-auxiliary inversion, \textit{wh}-words, etc.).

Children's anticipatory gaze switches were also affected by their age, but only in the non-English videos: 3- and 4-year-olds made many more anticipatory switches when watching videos in English compared to non-English, but this effect of language condition had attenuated significantly by age 5 (Table \ref{tab:E1-models};  Figure \ref{fig:E1-randvsreal}; Figure \ref{fig:E1-lgageinteraction}). This interaction suggests that the 5-year-olds were able to leverage anticipatory cues in the non-English videos in a way that 3- and 4-year-olds could not, possibly by shifting more attention to the non-native prosodic or non-verbal cues. Prior work on children's turn-structure anticipation proposed that children's turn-end predictions center on lexicosyntactic structure (and not, e.g., prosody) as they get older. The current results suggest more flexibility in children's predictions; when they do not have access to linguistic structure they are more likely to rely on alternative cues as they get older.

@@

Adults' anticipatory gaze rates were also affected by transition type, language condition, and gap duration (Table \ref{tab:E1-models}), none of which could be easily explained by a baseline of random gaze switching (Figure \ref{fig:E1-AduTs}). Like children, adults made more anticipatory switches after hearing questions compared to non-questions, suggesting that anticipation mattered more to them when an immediate response was expected. Also like children, the advantage for questions was driven by lexical access such that adults must have relied on lexicosyntactic cues to questionhood in picking out turns that potentially require an immediate response, though this effect was only marginally significant compared to the distribution of randomly permuted data (\textit{p} $=$ .053; Figure \ref{fig:E1-AduTs}). Finally, adults' anticipation rates were also affected by gap duration, but more so for questions than non-questions (Table \ref{tab:E1-models}). This interaction suggests that adults were less likely overall to make anticipatory switches at non-questions (as is evident for adults and children in Figure \ref{fig:E1-randvsreal}), and so did not benefit from extra time to do so compared to long gaps for questions.

@@

Children and adults' predictions alike were benefited by access to lexical information (English) and speech act status (questionhood), suggesting that linguistic cues, particularly lexical ones, facilitate their spontaneous predictions about upcoming turn structure through the identification of turns that will have immediate responses from the addressee. Children's anticipatory gaze rates for questions and non-questions in English was stable across ages and comparable to adult behavior (Figure \ref{fig:E1-randvsreal}), suggesting that they can identify questions in native stimuli with adult-like competence by age three. Although participants' ability to recognize questions was facilitated by lexical access (i.e., English vs. non-English), the prosody in the non-English videos was non-native, and so the experimental design can not conclusively show which linguistic cues children relied on in the English videos to identify question turns.

Relatedly, though lexical access clearly facilitated participants' anticipatory gaze rate, it was not necessary for participants, especially adults, in order to exceed chance switching rates (Figure \ref{fig:E1-randvsreal}), suggesting that participants use non-lexical cues (e.g., prosody, non-verbal behavior) to make anticipatory eye movements at least some of the time. In the case of adults there was no overall effect of language condition, only an interaction between language condition and transition type: adults spontaneously anticipated upcoming speakers whether they had lexical access or not, but when given lexical access, focused their anticipations on turns with immediate responses (questions).

Interestingly, adults and children both were strongly affected by transition type, in that they made more anticipatory switches after hearing questions, compared to non-questions. We had hypothesized that a projected response might affect participants' predictions but it in fact seems to be driving many of the effects in our data. Even in the English videos, when participants had full access to linguistic cues, their rates of anticipation were relatively low---in fact, comparable to the non-English videos---unless the turn was a question (Figure \ref{fig:E1-randvsreal}). Prior work using online, metalinguistic tasks has shows that participants can use linguistic cues to accurately predict upcoming turn ends. The current results suggest that, in their spontaneous predictions, both children and adults monitor the linguistic structure of unfolding turns for cues to upcoming responses. Because the form of an answer is partially determined by its question (e.g., locative expressions for ``where'' questions), participants could even be predicting what type of response they will hear, and so they are looking anticipatorily at the responder for confirmation of their prediction. This interpretation is initial, but in-line with work showing early response planning and speech act recognition \citep{gisladottir2015, bogels2015}.

Overall, children and adults behaved relatively similarly and our language manipulation (English vs. non-English) was too coarse to comment on when children begin to use different types of native linguistic cues (e.g., prosody vs. lexicosyntax); we would instead need to directly compare lexicosyntactic and prosodic cues in the participants' native language, controlling for the presence of non-verbal cues. To see the emergence of anticipatory gaze switching we would also need to include younger children since participants already reliably made anticipatory gaze switches at age three. In sum, Experiment 1 lays the analytic groundwork for a method that allows for greater experimental control, which we introduce in Experiment 2.

@@

We identified anticipatory gaze switches for all 85 usable turn transitions, and analyzed them for effects of language condition, transition type, and age with two mixed-effects logistic regressions \citep{lme4, R}. We again built separate models for children and adults because effects of age were only pertinent to the children's data. The child model included condition (normal/prosody only/words only/no speech; with no speech in the intercept), transition type (question vs. non-question), age (1, 2, 3, 4, 5, 6), and duration of the inter-turn gap (in seconds) as predictors, with full interactions between language condition, transition type, and age.  We again included the duration of the inter-turn gap as a control predictor and added random effects of item (turn transition) and participant, with random slopes of transition type for participants \citep{barr2013}. The adult model included condition, transition type, their interactions, and duration as a control predictor, with participant and item included as random effects and random slopes of condition and transition type.

Children's anticipatory gaze switches showed an effect of gap duration (\textit{$\beta$}=4.18, \textit{SE}=0.624, \textit{t}=6.689, \textit{p}$<$.001), a two-way interaction of age and language condition (for prosody only speech compared to the no speech intercept; \textit{$\beta$}=0.393, \textit{SE}=0.189, \textit{t}=2.08, \textit{p}$<$.05), and a three-way interaction of age, transition type, and language condition (for normal speech compared to the no speech intercept; \textit{$\beta$}=-0.375, \textit{SE}=0.17, \textit{t}=-2.213, \textit{p}$<$.05). There were no significant effects of age or transition type alone (Table \ref{sec:models}), with only a marginal effect of language condition (for prosody only compared to the no speech intercept; \textit{$\beta$}=-1.634, \textit{SE}=0.864, \textit{t}=-1.89, \textit{p}$=$.06)

Adults' anticipatory gaze switches showed effects of gap duration (\textit{$\beta$}=4.75, \textit{SE}=1.248, \textit{t}=3.806, \textit{p}$<$.001) and language condition (for normal speech \textit{$\beta$}=1.256, \textit{SE}=0.563, \textit{t}=2.229, \textit{p}$<$05. and words only speech \textit{$\beta$}=1.594, \textit{SE}=0.721, \textit{t}=2.211, \textit{p}$<$.05  compared to the no speech intercept). There were no effects of transition type (\textit{$\beta$}=0.429, \textit{SE}=0.609, \textit{t}=0.705, \textit{p}$=$.48).

@@

Using the same technique described in experiment 1 (Section \ref{sec:randbaseline1}), we created and modeled 5,000 random permutations of participants' anticipatory gaze. Our baseline analyses revealed that none of the significant predictors from models of the original, turn-related data (Table \ref{tab:E2-models}: Children) can be explained by random looking. In the children's data, the original \textit{t}-values for language condition (prosody only), gap duration, the two-way interaction of age and language condition (prosody only) and the three-way interaction of age, transition type, and language condition (normal only) were all greater than 95\% of the randomly permuted \textit{t}-value (96.2\%, 100\%, 95.1\%, and 95.1\%, respectively; Figure \ref{fig:E2-ChiTs}). Similarly, the adults' data showed significant differentiation from the randomly permuted data for all originally significant predictors: language condition for normal and words only speech and gap duration (greater than 96.8\%, 98.7\%, and 100\% of random \textit{t}-values, respectively; Figure \ref{fig:E2-AduTs}). The effects of language condition and transition type for the real and randomly permuted data can also be observed in Figure \ref{fig:E1-randvsreal}.

@@

\paragraph{Developmental effects}
The model of the children's data revealed two significant interactions with age, neither of which derived from random looking (Figure \ref{fig:E2-randvsreal}). The first was a significant interaction of age and language condition (for prosody only compared to the no speech baseline), suggesting a different age effect between the two linguistic conditions. As in Experiment 1, we further explored the age effect by extracting the average difference score over subjects for the interaction in each random permutation of the data, making pairwise comparisons between the six age groups. Figure \ref{fig:E2-lgageinteraction} shows the comparisons that demonstrate a significant difference in age for the no speech baseline vs. the prosody only condition, revealing that anticipatory gaze in the prosody only condition significantly improves with age, especially at ages 5 and 6, compared to the no-speech baseline (all with difference scores greater than 95\% of the random data scores; \textit{p} $<$ .05).

The second interaction with age was a three-way interaction of age, transition type, and language condition (for normal speech compared to the no speech baseline). We again created pairwise comparisons of the average difference scores for the interaction in each random permutation of the data, with significant differences shown in Figure \ref{fig:E2-lgagetypeinteraction}. These pairwise comparisons showed that the effect of transition type in the normal speech condition became larger with age, with significant improvements by age 4 over ages 1 and 2 (99.9\% and 98.86\%, respectively), by age 5 over age 4 (97.54\%), and by age 6 over ages 1, 2, and 5 (99.5\%, 97.36\%, and 95.04\%), all equating to significant differences from chance (\textit{p} $<$ .05).

\subsection{Discussion}
\label{sec:discussion2}

@@

\section{General Discussion}
\label{sec:gendisc}

>>>>

Each recording session began with a 20-minute warm-up period of spontaneous conversation during which the pair talked for five minutes on four topics (favorite foods, entertainment, hometown layout, and pets). Then we asked talkers to choose a new topic---one relevant to young children (e.g., riding a bike, eating breakfast)---and to improvise a dialogue on that topic. We asked them to speak as if they were on a children's television show in order to elicit child-directed speech toward each other. We recorded until the talkers achieved at least 30 seconds of uninterrupted discourse with enthusiastic, child-directed speech. Most talker pairs took less than five minutes to complete the task, usually by agreeing on a rough script at the start. We encouraged talkers to ask at least a few questions to each other during the improvisation. The resulting conversations were therefore not entirely spontaneous, but were as close as possible while still remaining child-oriented in topic, prosodic pattern, and lexicosyntactic construction.\footnote{All of the non-English talkers were fluent in English as a second language, and some fluently spoke a third or more language. We chose male-female pairs as a natural way of creating contrast between the two talker voices.}

@@

Participants looked at the screen most of the time during video playback (81\% and 91\% on average for children and adults, respectively). They primarily kept their eyes on the person who was currently speaking in both English and non-English videos: They gazed at the current speaker between 38\% and 63\% of the time, looking back at the addressee between 15\% and 20\% of the time (Table \ref{tab:e1_look}). Even three-year-olds looked more at the current speaker than anything else, whether the videos were in a language they could understand or not. Children looked at the current speaker less than adults did during the non-English videos. Despite this, their looks to the addressee did not increase substantially in the non-English videos, indicating that their looks away were probably related to boredom rather than confusion about ongoing turn structure. Overall, participants' pattern of gaze to current speakers demonstrated that they performed basic turn tracking during the videos, regardless of language.

@@

We identified anticipatory gaze switches for all 36 usable turn transitions, based on the criteria outlined in Section \ref{sec:algorithm}, and analyzed them for effects of language, transition type, and age with two mixed-effects logistic regressions \citep{lme4, R}. We built one model each for children and adults. We modeled children and adults separately because effects of age are only pertinent to the children's data. The child model included condition (English vs. non-English)\footnote{Because each non-English language was represented by a single stimulus, we cannot treat individual languages as factors. Gaze behavior might be best for non-native languages that have the most structural overlap with participants' native language: English speakers can make predictions about the strength of upcoming Swedish prosodic boundaries nearly as well as Swedish speakers do, but Chinese speakers are at a disadvantage in the same task \citep{carlson2005}. We would need multiple items from each of the languages to check for similarity effects of specific linguistic features.}, transition type (question vs. non-question), age (3, 4, 5), and duration of the inter-turn gap (seconds, e.g., 0.441) as predictors, with full interactions between condition, transition type, and age.  We included the duration of the inter-turn gap as a predictor since longer gaps also provide more opportunities to make anticipatory switches (Figure \ref{fig:criterion}). We additionally included random effects of item (turn transition) and participant, with random slopes of condition, transition type, and their interaction for participants \citep{barr2013}.\footnote{The models we report are all qualitatively unchanged by the exclusion of their random slopes. We have left the random slopes in because of minor participant-level variation in the predictors modeled.} The adult model included condition, transition type, duration, and their interactions as predictors with participant and item included as random effects and random slopes of condition, transition type, and their interaction for participant.

@@

We estimated the probability that these patterns were the result of random looking by running the same regression models on participants' real eye-tracking data, only this time calculating their anticipatory gaze switches with respect to randomly permuted turn transition windows. This process involved: (1) randomizing the order and temporal placement of the analysis windows within each stimulus (Figure \ref{fig:shuffling}; ``analysis window'' is defined in Figure \ref{fig:criterion}), thereby randomly redistributing the analysis windows across the eye-tracking signal, (2) re-running each participant's eye tracking data through switch identification (described in \ref{sec:algorithm}), this time using the randomly permuted analysis windows, and (3) modeling the anticipatory gazes from the randomly permuted data with the same statistical models we used for the original data (Section \ref{sec:models1}; Table \ref{tab:E1-models}). Importantly, although the onset time of each transition was shuffled within the eye-tracking signal, the other intrinsic properties of each turn transition (e.g., prior speaker identity, transition type, gap duration, language condition, etc.) stayed constant across each random permutation.

@@

\paragraph{Developmental effects}
The model of the children's data revealed a significant interaction of age and language condition (Table \ref{tab:E1-models}) that was highly unlikely to have derived from random looking (Figure \ref{fig:E1-randvsreal}). To further explore this effect, we compared the average effect of language condition across all ages: we extracted the average difference score for the two language conditions (English minus non-English) for each subject, computing an overall average for each random permutation of the data. For each random permutation, we then made pairwise comparisons of the average difference scores across ages. Figure \ref{fig:E1-lgageinteraction} plots the real-data difference scores against the random-data difference score distribution for each pairwise age comparison, showing that 3- and 4-year olds were affected equally by language condition, but that 5-year-olds affected less than both 3- and 4-year-olds (with 99.52\% and 99.96\% of difference scores greater than the randomly permuted data, respectively, i.e., differences of \textit{p} $<$ .01 and \textit{p} $<$ .001).

@@

Children and adults spontaneously tracked the turn structure of the conversations, making anticipatory gaze switches at an above-chance rate across all ages and conditions (Table \ref{tab:e1_look}; Figure \ref{fig:E1-randvsreal}). Children's anticipatory gaze rates were affected by language condition, transition type, age, and gap duration (Table \ref{tab:E1-models}), none of which could be explained by a baseline of random gaze switching (Figure \ref{fig:E1-ChiTs}).

Language condition (English vs. non-English) affected children's anticipations in two ways (Table \ref{tab:E1-models};  Figure \ref{fig:E1-randvsreal}). First, children made more anticipatory switches overall in English videos, compared to non-English videos. This effect suggests that lexical access is important for children's ability to anticipate upcoming turn structure; children had no lexical access to the speech in the non-English videos, though they did have access to (non-native) prosodic cues and non-verbal behavior, consistent with prior work on turn-end prediction in adults (\citealp{de-ruiter2006}; \citealp{magyari2012}) and children \citep{keitel2013}. Second, children systematically made more anticipatory switches after hearing a question compared to a non-question, but only in the English condition, suggesting that, when children have access to lexical cues, they are more likely to make an anticipatory gaze switch if they can expect an immediate response from the addressee. If so, then children's attention to lexical cues for turn taking may primarily be in monitoring the signal for cues to questionhood (e.g., subject-auxiliary inversion, \textit{wh}-words, etc.).

Children's anticipatory gaze switches were also affected by their age, but only in the non-English videos: 3- and 4-year-olds made many more anticipatory switches when watching videos in English compared to non-English, but this effect of language condition had attenuated significantly by age 5 (Table \ref{tab:E1-models};  Figure \ref{fig:E1-randvsreal}; Figure \ref{fig:E1-lgageinteraction}). This interaction suggests that the 5-year-olds were able to leverage anticipatory cues in the non-English videos in a way that 3- and 4-year-olds could not, possibly by shifting more attention to the non-native prosodic or non-verbal cues. Prior work on children's turn-structure anticipation proposed that children's turn-end predictions rely primarily on lexicosyntactic structure (and not, e.g., prosody) as they get older \citep{keitel2013}. The current results suggest more flexibility in children's predictions; when they do not have access to lexical information, older children are likely to find alternative cues to turn taking behavior.

@@

Adults' anticipatory gaze rates were also affected by transition type, language condition, and gap duration (Table \ref{tab:E1-models}), none of which could be easily explained by a baseline of random gaze switching (Figure \ref{fig:E1-AduTs}). Like children, adults made more anticipatory switches after hearing questions compared to non-questions, suggesting that anticipation mattered more to them when an immediate response was expected. Also like children, the advantage for questions was driven by lexical access such that adults must have relied on lexicosyntactic cues to questionhood in picking out turns that potentially require an immediate response, though this effect was only marginally divergent from the distribution of randomly permuted data (\textit{p} $=$ .053; Figure \ref{fig:E1-AduTs}). Finally, adults' anticipation rates were also affected by gap duration, but more so for questions than non-questions (Table \ref{tab:E1-models}). This interaction suggests that adults were less likely overall to make anticipatory switches at non-questions (as is evident for adults and children in Figure \ref{fig:E1-randvsreal}), and so did not benefit from extra time to do so compared to long gaps for questions.

@@

Children and adults' predictions alike were benefited by access to lexical information (English) and speech act status (questionhood), suggesting that linguistic cues, particularly lexical ones, facilitate their spontaneous predictions about upcoming turn structure through the identification of turns with immediate responses. Children's anticipatory gaze rates for questions and non-questions in English was stable across ages and comparable to adult behavior (Figure \ref{fig:E1-randvsreal}), suggesting that they can identify questions in native stimuli with adult-like competence by age three. Although participants' ability to recognize questions was facilitated by lexical access (i.e., English vs. non-English), the prosody in the non-English videos was non-native, and so the experimental design can not conclusively show which linguistic cues children relied on in the English videos to identify question turns. Relatedly, though lexical access clearly facilitated participants' anticipatory gaze rate, it was not necessary for participants---especially adults---in order to exceed chance switching rates (Figure \ref{fig:E1-randvsreal}), suggesting that participants use non-lexical cues (e.g., prosody, non-verbal behavior) to make anticipatory eye movements at least some of the time.

Interestingly, adults and children both were strongly affected by transition type, in that they made more anticipatory switches after hearing questions, compared to non-questions. Even in the English videos, when participants had full access to linguistic cues, their rates of anticipation were relatively low---in fact, comparable to the non-English videos---unless the turn was a question (Figure \ref{fig:E1-randvsreal}). Prior work using online, metalinguistic tasks has shows that participants can use linguistic cues to accurately predict upcoming turn ends. The current results suggest that, in their spontaneous predictions about third-party conversation, both children and adults monitor the linguistic structure of unfolding turns for cues to upcoming responses.

Children and adults generally behaved relatively similarly in this first experiment and our language manipulation (English vs. non-English) was too coarse to comment on when children begin to use different types of native linguistic cues (e.g., prosody vs. lexicosyntax); we would instead need to directly compare lexicosyntactic and prosodic cues in the participants' native language, controlling for the presence of non-verbal cues. To see the emergence of anticipatory gaze switching we would also need to include younger children, since participants already reliably made anticipatory gaze switches at age three. Experiment 1 thus lays the analytic groundwork for a method that allows for greater experimental control, which we introduce in Experiment 2.

@@

We identified anticipatory gaze switches for all 85 usable turn transitions, and analyzed them for effects of language condition, transition type, and age with two mixed-effects logistic regressions \citep{lme4, R}. We again built separate models for children and adults because effects of age were only pertinent to the children's data. The child model included condition (normal/prosody only/words only/no speech; with no speech as the reference level), transition type (question vs. non-question), age (1, 2, 3, 4, 5, 6), and duration of the inter-turn gap (in seconds) as predictors, with full interactions between language condition, transition type, and age.  We again included the duration of the inter-turn gap as a control predictor and added random effects of item (turn transition) and participant, with random slopes of transition type for participants \citep{barr2013}. The adult model included condition, transition type, their interactions, and duration as a control predictor, with participant and item included as random effects and random slopes of condition and transition type.

Children's anticipatory gaze switches showed an effect of gap duration (\textit{$\beta$}=4.18, \textit{SE}=0.624, \textit{t}=6.689, \textit{p}$<$.001), a two-way interaction of age and language condition (for prosody only speech compared to the no speech reference level; \textit{$\beta$}=0.393, \textit{SE}=0.189, \textit{t}=2.08, \textit{p}$<$.05), and a three-way interaction of age, transition type, and language condition (for normal speech compared to the no speech reference level; \textit{$\beta$}=-0.375, \textit{SE}=0.17, \textit{t}=-2.213, \textit{p}$<$.05). There were no significant effects of age or transition type alone (Table \ref{sec:models2}), with only a marginal effect of language condition (for prosody only compared to the no speech reference level; \textit{$\beta$}=-1.634, \textit{SE}=0.864, \textit{t}=-1.89, \textit{p}$=$.06)

Adults' anticipatory gaze switches showed effects of gap duration (\textit{$\beta$}=4.75, \textit{SE}=1.248, \textit{t}=3.806, \textit{p}$<$.001) and language condition (for normal speech \textit{$\beta$}=1.256, \textit{SE}=0.563, \textit{t}=2.229, \textit{p}$<$05. and words only speech \textit{$\beta$}=1.594, \textit{SE}=0.721, \textit{t}=2.211, \textit{p}$<$.05  compared to the no speech reference level). There were no effects of transition type (\textit{$\beta$}=0.429, \textit{SE}=0.609, \textit{t}=0.705, \textit{p}$=$.48).

@@

Using the same technique described in experiment 1 (Section \ref{sec:randbaseline1}), we created and modeled 5,000 random permutations of participants' anticipatory gaze. Our baseline analyses revealed that none of the significant predictors from models of the original, turn-related data (Table \ref{tab:E2-models}: Children) can be explained by random looking. In the children's data, the original model's \textit{t}-values for language condition (prosody only), gap duration, the two-way interaction of age and language condition (prosody only) and the three-way interaction of age, transition type, and language condition (normal speech) were all greater than 95\% of the randomly permuted \textit{t}-values (96.2\%, 100\%, 95.1\%, and 95.1\%, respectively; Figure \ref{fig:E2-ChiTs}). Similarly, the adults' data showed significant differentiation from the randomly permuted data for all originally significant predictors: gap duration and language condition for normal speech and words-only speech (greater than 100\%, 96.8\%, and 98.7\% of random \textit{t}-values, respectively; Figure \ref{fig:E2-AduTs}). The effects of language condition and transition type for the real and randomly permuted data can also be observed in Figure \ref{fig:E1-randvsreal}.

@@

\paragraph{Developmental effects}
The model of the children's data revealed two significant interactions with age, neither of which derived from random looking (Table \ref{tab:E2-models}; Figure \ref{fig:E2-randvsreal}). The first was a significant interaction of age and language condition (for prosody only compared to the no speech reference level), suggesting a different age effect between the two linguistic conditions. As in Experiment 1, we further explored the age effect by extracting the average difference score over subjects for this age-language condition interaction in each random permutation of the data, making pairwise comparisons between the six age groups. Figure \ref{fig:E2-lgageinteraction} shows the comparisons that demonstrate a significant difference in age for the no speech baseline vs. the prosody only condition, revealing that anticipatory gaze in the prosody only condition significantly improves with age, especially at ages 5 and 6 (all with difference scores greater than 95\% of the random data scores; \textit{p} $<$ .05).

The second interaction with age was a three-way interaction of age, transition type, and language condition (for normal speech compared to the no speech baseline). We again created pairwise comparisons of the average difference scores for this age-transition type-language condition interaction in each random permutation of the data, with significant differences shown in Figure \ref{fig:E2-lgagetypeinteraction}. These pairwise comparisons showed that the effect of transition type in the normal speech condition became larger with age, with significant improvements by age 4 over ages 1 and 2 (99.9\% and 98.86\%, respectively), by age 5 over age 4 (97.54\%), and by age 6 over ages 1, 2, and 5 (99.5\%, 97.36\%, and 95.04\%), all significantly different from chance (\textit{p} $<$ .05).

\subsection{Discussion}
\label{sec:discussion2}
As in Experiment 1, children and adults spontaneously tracked the turn structure of the conversations, making anticipatory gaze switches at an above-chance rate across all ages but not in all conditions (Table \ref{tab:e2_look}; Figure \ref{fig:E2-randvsreal}). In the normal speech condition, however, when children had access to full linguistic information, they made more anticipatory gaze switches than expected by chance even at age one. Children's anticipatory gaze rates were affected by gap duration, plus interactions of language condition, transition type and age (Table \ref{tab:E2-models}), none of which could be explained by a baseline of random gaze switching (Figure \ref{fig:E2-ChiTs}).

Two of the three linguistic conditions affected children's anticipatory gaze switches, compared to the no-speech reference level: prosody-only speech and normal speech. Prosody only speech resulted in fewer anticipatory gazes overall, compared to the no-speech baseline, though the effect was only marginal (\textit{p}$=$.06). However, prosody-only speech \textit{did} significantly differ from the no speech condition in its interaction with age: whereas age gains were negligible in the no speech condition, 5- and 6-year-olds in the prosody-only condition showed significantly more anticipatory gaze switches than younger children (Figure \ref{fig:E2-lgageinteraction}), going from below- and at-chance anticipatory gaze rates to being well above chance (Figure \ref{fig:E2-randvsreal}).

The normal speech condition showed a significantly more gains in anticipatory gaze for questions with age compared to the no-speech condition. As in Experiment 1, children consistently made more anticipatory gazes after hearing questions when they had access to lexical material. But now, with a larger age span in Experiment 2, we can begin to see a developmental path for the question effect. At least for normal speech, greater anticipatory looking for questions is not present from the start: 4-year-olds are the first to make significant gains on 1- and 2-year-olds, but then there are further significant gains at age 5, and again age 6 (Figure \ref{fig:E2-lgagetypeinteraction}). While children at ages five and six showed adult-like differentiation of questions and non-questions in the normal speech condition, 1-year-olds had nearly identical switch rates for the two transition types. This suggests that the participants' tendency to make more anticipatory switches for questions emerges after age one and continues developing, with rapid gains in ages three through age six. Finally, children showed a straightforward effect of gap duration (Table \ref{tab:E2-models}), as in Experiment 1.

Adults' anticipatory gaze rates were affected by gap duration and two of the language conditions (Table \ref{tab:E2-models}), none of which could be explained by a baseline of random gaze switching (Figure \ref{fig:E2-AduTs}). Adults made more anticipatory switches overall for the normal speech and words-only conditions compared to the no-speech condition, falling in-line with past work showing that adults primarily use lexical information in making predictions about upcoming turn structure \citep{de-ruiter2006}. Though adults did make more anticipatory switches for questions than non-questions on average in the two lexical conditions (Figure \ref{fig:E2-randvsreal}), the effect of transition type was not significant in either (Table \ref{tab:E2-models}), unlike Experiment 1. Like children, adults also showed a straightforward effect of gap duration.

@@

\section{General Discussion}
\label{sec:gendisc}

% CAN USE LATER: Because the form of an answer is partially determined by its question (e.g., locative expressions for ``where'' questions), participants could even be predicting what type of response they will hear, and so they are looking anticipatorily at the responder for confirmation of their prediction. This interpretation is initial, but in-line with work showing early response planning and speech act recognition \citep{gisladottir2015, bogels2015}.
